%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cleaned and Refactored Resume Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper]{article}

% --- Packages ---
\usepackage[top=0.3in, bottom=0.3in, left=0.5in, right=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{tcolorbox}
\usepackage{array}
\usepackage{helvet} % For sans-serif font
\renewcommand{\familydefault}{\sfdefault}

% --- Custom Formatting ---
\definecolor{lightgray}{gray}{0.9}

% Section Box Definition (tcolorbox)
\newtcolorbox{sectionbox}{
    colback=lightgray,
    colframe=white,
    boxrule=0pt,
    arc=0pt,
    left=4pt,
    right=4pt,
    top=1pt,
    bottom=1pt,
    width=\dimexpr\textwidth\relax
}

% Hyperlink Setup
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

% General Spacing Adjustments
\setlength{\tabcolsep}{2pt}
\renewcommand{\arraystretch}{0.9}
\setlist[itemize]{
    leftmargin=1.5em, 
    topsep=0pt, 
    partopsep=0pt, 
    itemsep=0.5pt, 
    parsep=0pt
}
\titlespacing{\section}{0pt}{0.5pt}{0.5pt}
\setlength{\parskip}{0pt} % Ensure paragraphs don't have extra space

% --- Custom Commands for Content Consistency ---

% Command for Sub-headings (e.g., Job/Project Title)
% Usage: \resumesubheading{Title}{Company/Location}{Dates}
\newcommand{\resumesubheading}[3]{
    \vspace{0em}
    \begin{tabularx}{\textwidth}{@{}X r@{}}
        \textbf{#1 | #2} & #3 \\
    \end{tabularx}
    \vspace{-0.2em}
}

% Command for Bullet Points
\newcommand{\resumeitem}[1]{\item #1}


% --- Document Start ---
\begin{document}
\vspace*{-0.3cm}

% ===================================
% CONTACT / HEADER
% ===================================
\begin{center}
    {\LARGE\bfseries ANUSHKA RATHORE}
    \\[2pt] % Small space
    Department of Electronics and Communication, NSUT DELHI $\vert$ +91 9650229342 $\vert$ \href{mailto:anushka.rathoreOfficial@gmail.com}{anushka.rathoreOfficial@gmail.com}\\
    \href{https://linkedin.com/in/anushkarathore}{LinkedIn}
\end{center}

% ===================================
% ACADEMIC QUALIFICATIONS
% ===================================
\begin{sectionbox}\textbf{ACADEMIC QUALIFICATIONS}\end{sectionbox}
\vspace{-0.3em}
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \textbf{Netaji Subhas University of Technology}, Delhi & 2022 -- 2026 \\
    B.Tech & CGPA: \textbf{[To be filled]}\\ % <<<-- FIX APPLIED HERE
\end{tabular*}
\vspace{-0.3em}
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \textbf{Shanti Gyan International}, Delhi & 2022 \\
    CBSE (XII) & 9.4 \\[0.5em]
    \textbf{Amity International School}, Noida & 2020 \\
    CBSE (X) & 10 \\
\end{tabular*}

% ===================================
% WORK EXPERIENCE
% ===================================
\begin{sectionbox}\textbf{WORK EXPERIENCE}\end{sectionbox}

\resumesubheading{Research Intern}{DRDO, Ministry of Defence}{May'25 -- Jul'25}
\textit{DRDO, Ministry of Defence}
\vspace{-0.2em}
\begin{itemize}
    \resumeitem{Designed and automated key operational dashboards using Power BI to track inventory and safety compliance metrics, reducing manual report generation time by 90\%.}
    \resumeitem{Developed full-stack web applications and geospatial site-selection tools improving data accuracy and support for strategic facility planning.}
    \resumeitem{Delivered budgeting and forecasting dashboards enhancing decision-making efficiency and operational SLA adherence for explosive facility management.}
\end{itemize}
\vspace{0.4em}

\resumesubheading{Business Analyst Intern}{Agya Group}{Jan'25 -- Mar'25}
\textit{Agya Group}
\vspace{-0.2em}
\begin{itemize}
    \resumeitem{Conducted SQL-driven regional client segmentation and competitor analysis, enabling targeted outreach that expanded the B2B network by 25\% within three months.}
    \resumeitem{Generated actionable reports tracking international agri-export market trends, leading to 5 qualified leads and identification of 3 high-potential growth opportunities.}
    \resumeitem{Produced stakeholder engagement dashboards monitoring agent activity and sales pipelines, improving forecast accuracy and process efficiency.}
\end{itemize}

% ===================================
% KEY PROJECTS
% ===================================
\begin{sectionbox}\textbf{KEY PROJECTS}\end{sectionbox}

\resumesubheading{Coffee Shop Sales Dashboard | Link}{(Excel, Power BI, SQL)}{}
\vspace{-0.2em}
\begin{itemize}
    \resumeitem{Engineered a Power BI sales dashboard analyzing 9,900+ transactions with real-time filters by time and city, improving revenue and profit KPI tracking.}
    \resumeitem{Cleansed and standardized SQL datasets resolving join conflicts, enabling automated, error-free reporting for daily sales performance monitoring.}
\end{itemize}
\vspace{0.4em}

\resumesubheading{Cars24 Analysis | Link}{(Excel, Tableau, Google Sheets, SQL, Python)}{}
\vspace{-0.2em}
\begin{itemize}
    \resumeitem{Analyzed 6,206 loan and card applications; identified 63\% login drop-offs and 85\% application abandonment points to optimize customer engagement.}
    \resumeitem{Recommended strategic shifts and ROI-aligned initiatives projecting a 20\% increase in loan disbursals and enhanced service-level compliance.}
\end{itemize}
\vspace{0.4em}

\resumesubheading{Agricultural \& Climatic Data Analytics Pipeline | Link}{(AWS S3, Snowflake, Power BI, MS Excel)}{}
\vspace{-0.2em}
\begin{itemize}
    \resumeitem{Constructed a cloud-based ETL pipeline using AWS S3 and Snowflake, optimizing large datasets with advanced SQL transformations for efficient query performance.}
    \resumeitem{Developed intuitive Power BI dashboards using DAX to monitor rainfall, temperature, humidity, and yield trends, supporting real-time monitoring and forecasting.}
\end{itemize}

% ===================================
% TECHNICAL SKILLS
% ===================================
\begin{sectionbox}\textbf{TECHNICAL SKILLS}\end{sectionbox}
\vspace{0em}
% Used tabularx for clean alignment
\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}
    Programming \& Data Analysis: & Python (NumPy, Pandas, Matplotlib), SQL \\
    Data Visualization \& BI: & MSPowerPoint, Power BI, Tableau, MS Excel (Pivot Tables, Power Query, Macros), Google Sheets (App Script) \\
    Cloud \& Databases: & Snowflake, AWS S3, Supabase, MongoDB \\
    Product \& Consulting: & Figma, Canva, Jira \\
    AI Tools: & ChatGPT, Claude, Grok, Notebook LM, Merlin, AnySummary, Napkin.ai, Gamma.app, Julius AI, Notion AI \\
\end{tabularx}

% ===================================
% POSITIONS OF RESPONSIBILITY
% ===================================
\begin{sectionbox}\textbf{POSITIONS OF RESPONSIBILITY}\end{sectionbox}
\resumesubheading{Director}{Crosslinks NSUT}{Aug'23 -- May'24}
\begin{itemize}
    \resumeitem{Led a team of 50+ students to deliver a 130-page yearbook, coordinating seamlessly with faculty and Dean while ensuring deadlines and content accuracy.}
    \resumeitem{Managed social media channels (Quora, YouTube, LinkedIn, Instagram) with 9.5k+ followers, creating 15+ posts and securing ₹30,000 sponsorships via cold calls.}
    \resumeitem{Organized and coordinated 3 large-scale events with 1,000+ attendees, optimizing resource allocation and participant engagement.}
\end{itemize}

% ===================================
% CERTIFICATIONS AND ACHIEVEMENTS
% ===================================
\begin{sectionbox}\textbf{CERTIFICATIONS}\end{sectionbox}
\vspace{0em}
\begin{itemize}
    \resumeitem{Power BI Workshop by United Latino Students Association}
    \resumeitem{Become a Product Manager by Udemy}
    \resumeitem{Data Analytics Job Simulation by Deloitte Australia}
    \resumeitem{23 In-Demand AI Applications \& Tools by Be10X IITK}
\end{itemize}

\begin{sectionbox}\textbf{ACHIEVEMENTS}\end{sectionbox}
\vspace{0em}
\begin{itemize}
    \resumeitem{Ranked Top 0.01\% among 30,000+ teams in Myntra WeForShe Competition. | Link}
    \resumeitem{Ranked Top 500 out of 30,000 participants in ISRO SPOT prelims.}
    \resumeitem{Achieved ACC Cadet status.}
\end{itemize}

\end{document}
