\documentclass[a4paper]{article}\usepackage[top=0.3in, bottom=0.3in, left=0.5in, right=0.5in]{geometry}\usepackage{titlesec}\usepackage{enumitem}\usepackage{hyperref}\usepackage{parskip}\usepackage{xcolor}\usepackage{multicol}\usepackage{tabularx}\usepackage{tcolorbox}\usepackage{array}\usepackage{helvet}\usepackage{calc}\renewcommand{\familydefault}{\sfdefault}\definecolor{lightgray}{gray}{0.9}\newtcolorbox{sectionbox}{colback=lightgray,colframe=white,boxrule=0pt,arc=0pt,left=4pt,right=4pt,top=1pt,bottom=1pt,width=\dimexpr\textwidth\relax}\hypersetup{colorlinks=true,urlcolor=blue,linkcolor=black}\setlength{\tabcolsep}{2pt}\renewcommand{\arraystretch}{0.9}\setlist[itemize]{leftmargin=1.5em,topsep=0pt,partopsep=0pt,itemsep=0.5pt,parsep=0pt}\titlespacing{\section}{0pt}{0.5pt}{0.5pt}\setlength{\parskip}{0pt}\begin{document}\vspace*{-0.3cm}\begin{center}{\LARGE\bfseries [Candidate Name]}\\ [City, State] \textbar\ [Phone Number] \textbar\ \href{mailto:[Email Address]}{[Email Address]}\\ \href{https://linkedin.com/in/johndoe}{linkedin.com/in/johndoe} \textbar\ \href{https://github.com/johndoe}{github.com/johndoe}\end{center}\vspace{-0.3em}\begin{itemize}\item Results-driven professional with expertise in [Industry/Field relevant to role], leveraging proven skills in [Key skills aligned with job description]. Demonstrated ability to deliver measurable improvements and contribute to company growth.\end{itemize}\begin{sectionbox}\textbf{EDUCATION}\end{sectionbox}\vspace{-0.3em}\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}\textbf{[Institution]} & [Graduation Year]\\ [Degree] & \\\end{tabular*}\begin{sectionbox}\textbf{INTERNSHIPS AND EXPERIENCE}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{[Position Title]}, [Current/Most Recent Employer] & [Month Year] -- Present \\ \textit{} & \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Lead and manage [specific function or team], driving [relevant process or project area] resulting in [quantifiable achievement, e.g., "15\% increase in efficiency over 12 months"].\item Collaborate cross-functionally to design and implement [specific system/process], applying [job description keywords e.g., "data analysis", "strategic planning", "stakeholder management"] to enhance outcomes.\item Develop and execute [project or initiative], achieving [metric such as "a 20\% cost reduction" or "30\% revenue growth"], directly supporting organizational objectives.\item Utilize [software/tools/techniques] to streamline operations, boosting productivity by [measurable impact].\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{[Position Title]}, [Previous Employer] & [Month Year] -- [Month Year] \\ \textit{} & \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Directed and optimized [specific workflow/process] aligning with industry best practices and the company's mission, resulting in [specific achievement].\item Partnered with [teams, vendors, or clients] to deliver [product/service], contributing to increased [customer satisfaction, retention, revenue] by [metric].\item Applied [required skill/technology from job description] to solve complex challenges and enhance project delivery.\item Mentored junior staff, fostering skill development aligned with company culture and values.\end{itemize}\begin{sectionbox}\textbf{SKILLS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}} Core Competencies: & [Relevant skills/technologies aligned with job description, e.g., "Project Management, SQL, Agile methodologies"] \\\end{tabularx}\begin{sectionbox}\textbf{PROJECTS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{ExpenseTracker Pro (Personal Project)} & \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item Built a CLI-based personal expense tracker.\item Implemented persistent storage using SQLite3 for 5K+ entries.\item \textbf{Tech Stack:} Python, SQLite3, Pandas \end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Data Visualization Dashboard (Team Project)} & \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item Designed and deployed a Power BI dashboard for retail sales analysis.\item Automated ETL using Excel macros and SQL scripts.\item Reduced report generation time by \textbf{55\%}. \end{itemize}\begin{sectionbox}\textbf{POSITIONS OF RESPONSIBILITY}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{President, Tech Club – NSUT} & 2023 -- 2024 \\\end{tabularx}\begin{itemize}\item Led a 15-member tech team organizing coding hackathons and seminars.\item Increased participation by \textbf{100\%} through online campaigns and events.\end{itemize}\vspace{0.3em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Coordinator, Data Science Society} & 2022 -- 2023 \\\end{tabularx}\begin{itemize}\item Managed operations for 10+ workshops on analytics and visualization.\item Raised sponsorship worth \pounds 50K by collaborating with industry partners.\end{itemize}\begin{sectionbox}\textbf{EXTRA-CURRICULARS \& ACHIEVEMENTS}\end{sectionbox}\vspace{0em}\begin{itemize}\item 2nd place at National DataHack 2024 among 400+ participants.\item Awarded for excellence in automation and leadership initiatives.\item Represented university in state-level Table Tennis championship.\item \textbf{Certifications:} [List certifications if provided]\item \textbf{Additional Information:} [Languages, volunteer work, or other information if applicable]\end{itemize}\end{document}