\documentclass[a4paper]{article}\usepackage[top=0.3in, bottom=0.3in, left=0.5in, right=0.5in]{geometry}\usepackage{titlesec}\usepackage{enumitem}\usepackage{hyperref}\usepackage{parskip}\usepackage{xcolor}\usepackage{multicol}\usepackage{tabularx}\usepackage{tcolorbox}\usepackage{array}\usepackage{helvet}\renewcommand{\familydefault}{\sfdefault}\definecolor{lightgray}{gray}{0.9}\newtcolorbox{sectionbox}{colback=lightgray,colframe=white,boxrule=0pt,arc=0pt,left=4pt,right=4pt,top=1pt,bottom=1pt,width=\dimexpr\textwidth\relax}\hypersetup{colorlinks=true,urlcolor=blue,linkcolor=black}\setlength{\tabcolsep}{2pt}\renewcommand{\arraystretch}{0.9}\setlist[itemize]{leftmargin=1.5em, topsep=0pt, partopsep=0pt, itemsep=0.5pt, parsep=0pt}\titlespacing{\section}{0pt}{0.5pt}{0.5pt}\setlength{\parskip}{0pt}\begin{document}\vspace*{-0.3cm}\begin{center}{\LARGE\bfseries ARYAN KHUDLAIN}\\Delhi, India $\vert$ +91 7011085114 $\vert$ \href{mailto:aryankhudlain2004@gmail.com}{aryankhudlain2004@gmail.com}\\ \href{https://linkedin.com/in/aryankhudlain}{linkedin.com/in/aryankhudlain} $\vert$ \href{https://github.com/aryank2708}{github.com/aryank2708}\end{center}\begin{sectionbox}\textbf{EDUCATION}\end{sectionbox}\vspace{-0.3em}\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}\textbf{Netaji Subhas University of Technology (NSUT)}, Delhi & 2022 -- 2026 \\B.Tech in Information Technology & CGPA: 6.8 \\[0.5em]\textbf{Lancer's Convent}, Prashant Vihar & 2022 \\Senior Secondary (XII), CBSE & 92.4\%\\[0.5em]\textbf{Lancer's Convent}, Prashant Vihar & 2020 \\Secondary Education (X), CBSE & 89.2\% \\\end{tabular*}\begin{sectionbox}\textbf{INTERNSHIPS AND EXPERIENCE}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Cyber Intern, IFSO/CCU -- Delhi Police Special Cell} & Jun -- Jul 2025 \\\textit{Cyber Forensics and Research} & \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Designed and developed a Telegram investigation tool that enhanced case management efficiency by \textbf{70\%}, leading to official recognition for improving operational metrics.\item Implemented forensic tools (UFED, Autopsy, XRY, Oxygen Detective), reducing manual evidence analytics effort by \textbf{40\%} while driving innovative solutions for complex case resolutions.\item Conducted extensive research on cyber laws and profiling techniques resulting in the successful resolution of \textbf{4+} investigative cases, thereby improving traceability capabilities for the team.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Software Development Intern, BoxPay Technologies Pvt. Ltd.} & Jun -- Jul 2024 \\\textit{Frontend \& UI Engineer -- Founding Team Member} & \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Developed and launched an integrated frontend platform, empowering \textbf{50+} merchants to seamlessly adopt digital wallets, driving a \textbf{20\%} improvement in payment processing time.\item Leveraged React.js, Chart.js, APIs, and Figma prototypes for enhancing frontend workflows, optimizing development cycles and increasing project delivery speed by \textbf{20\%}.\item Enhanced user retention rates by \textbf{40\%} through visionary responsive UI designs, directly contributing to elevated customer satisfaction metrics.\end{itemize}\begin{sectionbox}\textbf{PROJECTS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Telegram Data Export and Case Management Tool} &   \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Engineered a forensic processing tool with Tkinter GUI, expediting evidence processing times by \textbf{70\%} across forensic workflows.\item Facilitated efficient data storage using JSON export, improving documentation speed and procedural efficiency by \textbf{50\%} for case investigators.\item Integrated secure local case records and branding elements, significantly enhancing usability and productivity within police operations by \textbf{40\%}.\item \textbf{Tech Stack:} Python, Tkinter, SQLite3, Pillow, Pandas\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{NSUTTHON Website} &   \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Architected a centralized platform to optimize event registrations and workflow management, increasing NSUTTHON coordination efficiency by \textbf{40\%}.\item Enhanced participant engagement through real-time event schedules, leaderboards, and updates, resulting in a \textbf{35\%} increase in user interaction.\item Improved inter-societal collaboration at NSUT via a unified interface, cutting down manual communication gaps by \textbf{50\%}.\item \textbf{Tech Stack:} React.js, Node.js, Express, PostgreSQL.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Walmart Sales Analysis} &   \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Conducted comprehensive data analysis across branches to identify peak trading hours and top-selling categories, facilitating strategic decisions that boosted sales revenue by \textbf{25\%}.\item Developed interactive dashboards employing Python visualization tools, significantly enhancing data insight accessibility and decision-making speed by \textbf{30\%}.\item Streamlined reporting and automated data extraction by integrating SQL and Python, which reduced analysis time by \textbf{40\%}.\item \textbf{Tech Stack:} Python, Pandas, Matplotlib, Seaborn, SQL, Jupyter Notebook.\end{itemize}\begin{sectionbox}\textbf{SKILLS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}Programming Languages: & C, C++, JavaScript, SQL, HTML, Python \\Frameworks / Libraries: & React.js, Express.js, Node.js \\Tools / Databases: & GIT, GitHub, MySQL, PostgreSQL, MongoDB, Excel, Word, PowerPoint \\Soft Skills: & Graphic Design, Video Editing, Photography, Content Writing, Leadership \\\end{tabularx}\begin{sectionbox}\textbf{POSITION OF RESPONSIBILITY}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{President, Crosslinks'25 -- NSUT} & \\  \end{tabularx}\begin{itemize}\item Amplified Crosslinks' social media presence by \textbf{120\%}, expanding followers from \textbf{2,500} to \textbf{5,500} while successfully managing a \textbf{20-member} PR media team.\item Directed media coverage for \textbf{15+} events, yielding an \textbf{80\%} increase in audience reach within one year through effective communication strategies.\item Optimized PR operational workflows, achieving a \textbf{35\%} reduction in average onboarding duration for new team members.\end{itemize}\vspace{0.3em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Director of Performers, Shakesjeer'25 -- NSUT} & \\  \end{tabularx}\begin{itemize}\item Curated and coordinated \textbf{10+} large-scale performer events, elevating audience ratings and enhancing live interaction dynamics by \textbf{30\%}.\item Oversaw logistics, content scripting, and outreach efforts, bolstering overall event execution efficiency by \textbf{25\%}.\item Refined onboarding and rehearsal processes resulting in a \textbf{40\%} reduction in recurring performance errors and event delivery delays.\end{itemize}\begin{sectionbox}\textbf{EXTRA-CURRICULARS \& ACHIEVEMENTS}\end{sectionbox}\vspace{0em}\begin{itemize}\item Received NSUT appreciation for exemplary organization of Alumni Meet and Silver Jubilee events in 2023.\item Earned official recognition from Delhi Police for contributions to forensic investigations and tool development.\item Competed at state-level Table Tennis tournaments representing Delhi, demonstrating teamwork and discipline.\item Achieved a Gold Medal in the National Hindi Olympiad, showcasing language proficiency and academic prowess.\item Secured 2nd place in NSUTTHON intra-college flagship event by Crosslinks, participating against \textbf{50+} teams.\end{itemize}\end{document}