\documentclass[a4paper]{article}\usepackage[top=0.3in, bottom=0.3in, left=0.5in, right=0.5in]{geometry}\usepackage{titlesec}\usepackage{enumitem}\usepackage{hyperref}\usepackage{parskip}\usepackage{xcolor}\usepackage{multicol}\usepackage{tabularx}\usepackage{tcolorbox}\usepackage{array}\usepackage{helvet}\renewcommand{\familydefault}{\sfdefault}\definecolor{lightgray}{gray}{0.9}\newtcolorbox{sectionbox}{colback=lightgray, colframe=white, boxrule=0pt, arc=0pt, left=4pt, right=4pt, top=1pt, bottom=1pt, width=\dimexpr\textwidth\relax}\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}\setlength{\tabcolsep}{2pt}\renewcommand{\arraystretch}{0.9}\setlist[itemize]{leftmargin=1.5em, topsep=0pt, partopsep=0pt, itemsep=0.5pt, parsep=0pt}\titlespacing{\section}{0pt}{0.5pt}{0.5pt}\setlength{\parskip}{0pt}\begin{document}\vspace*{-0.3cm}\begin{center}{\LARGE\bfseries Kushal Goyal}\\+91-9718940817 $\vert$ \href{mailto:kushalgoyal48@gmail.com}{kushalgoyal48@gmail.com} $\vert$ \href{https://linkedin.com/in/kushal-goyal-300522249}{linkedin.com/in/kushal-goyal-300522249} $\vert$ \href{https://github.com/KUSHALGOYALT}{github.com/KUSHALGOYALT}\end{center}\begin{sectionbox}\textbf{EDUCATION}\end{sectionbox}\vspace{-0.3em}\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}\textbf{Bharati Vidyapeeth's College of Engineering, GGSIPU, New Delhi} & 2022 -- 2026 \\B.Tech. in Computer Science & CGPA: 8.0 \\\end{tabular*}\vspace{0.5em}\begin{sectionbox}\textbf{CERTIFICATIONS}\end{sectionbox}\vspace{-0.2em}\begin{itemize}\item Spring Boot \& Spring AI (Telusko), C++ \& DSA (Coding Ninjas)\end{itemize}\begin{sectionbox}\textbf{INTERNSHIPS AND EXPERIENCE}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{SDE Intern – Hexa Climate Solutions Pvt. Ltd., New Delhi} & Jul 2025 -- Present \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item Developed and maintained scalable Python backend services using Django, supporting 1,000+ active monthly users with reliable API integrations.\item Designed and deployed a secure QR code generator automating 110+ workflow tasks, reducing manual effort by 25\% and saving 3+ hours weekly.\item Built an NLP-powered Terms \& Conditions Chatbot with prompt engineering techniques, improving client onboarding speed by 30\% for 200+ users.\item Engineered React.js dashboards enabling real-time user analytics, improving visibility by 40\% and adhering to accessibility and UI best practices.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Backend Intern – Secuverse Technologies Pvt. Ltd. (Remote)} & Jun 2025 -- Aug 2025 \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item Engineered FastAPI backend processing 100,000+ telecom records for forensic crime analysis, optimizing data flow with REST API design.\item Streamlined linkage analytics pipelines, cutting data processing time by 35\% through algorithmic and code refactoring enhancements.\item Refactored legacy Python modules, improving code maintainability and reducing complexity by 30\%, following clean coding and version control (Git) standards.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Intel Unnati Summer Training (Remote)} & May 2025 -- Jul 2025 \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item Architected backend infrastructure with Flask and Spring Boot, reducing query latency by 30\% via efficient API design and microservices architecture.\item Developed REST APIs supporting real-time Q\&A for 500+ users and integrated SWOT analysis, ensuring scalable and efficient system performance.\item Implemented secure authentication system using Java and Firebase, enhancing modularity by 25\% and improving user management.\item Led remote team collaboration enhancing sprint delivery success rate by 15\%, practicing agile methodologies and effective communication.\end{itemize}\begin{sectionbox}\textbf{SKILLS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}Programming Languages: & Python, Java, C++ \\Cloud \& Tools: & Docker, Git, Power BI, Excel \\Data Analytics \& Visualization: & Python (Pandas, Matplotlib, Seaborn), Statistical Analytics \\Web/Backend: & Django, FastAPI, Flask, Spring Boot, REST APIs, JWT, Microservices \\Databases: & SQL, MongoDB, Firebase \\Frontend: & React.js, HTML5, CSS3, JavaScript, Streamlit (familiarity) \\Core Concepts: & Data Structures \& Algorithms, Operating System, Software Engineering, System Design \\\end{tabularx}\begin{sectionbox}\textbf{PROJECTS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{LearnSphere – AI-Powered Learning Assistant (Spring Boot, Python, AI)} & \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item \href{https://github.com/KUSHALGOYALT/Thinkin1}{github.com/KUSHALGOYALT/Thinkin1}\item Launched multimodal EdTech platform personalizing content for 100+ students leveraging AI models for text, voice, and image processing.\item Created interactive dashboards reporting educator performance with 35\% improved engagement metrics using data visualization tools.\item Automated academic workflows, increasing syllabus content delivery speed by 50\%, improving user satisfaction and platform scalability.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Skill Swap - Peer-to-Peer Platform (Java Spring, React.js, AI)} & \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item \href{https://github.com/KUSHALGOYALT/Skill-swap}{github.com/KUSHALGOYALT/Skill-swap}\item Deployed skill exchange platform supporting 100+ concurrent users, integrating real-time messaging and calls with React.js frontend.\item Enhanced security via RBAC and Java Spring authentication modules, ensuring data privacy and compliance with best practices.\item Developed AI-driven skill matchmaking algorithm combining collaborative filtering and NLP, increasing match accuracy by 20\%, enhancing user retention.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Export Management Platform (Spring Framework, Data Analytics)} & \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item \href{https://github.com/KUSHALGOYALT/amazonsambhav}{github.com/KUSHALGOYALT/amazonsambhav}\item Developed KPI comparison platform integrating shipment APIs, accelerating decision-making by 60\% through analytics and dashboard automation.\item Delivered Spring Framework web app supporting 3 user roles and 500+ active users with secure access and robust backend.\item Created Power BI dashboards ranked Top 10 at Amazon Shambhav 2024 among 100k+ participants, demonstrating data-driven impact.\end{itemize}\begin{sectionbox}\textbf{LEADERSHIP \& ACHIEVEMENTS}\end{sectionbox}\vspace{0em}\begin{itemize}\item Spearheaded IEEE IAS BVCOE chapter as Chairperson, mentoring 25+ peers in DSA and software engineering, boosting coding proficiency by 15\%.\item Secured \$150 sponsorship for GeeksforGeeks College Society, enhancing event resources and participation.\item Top 10 Finalist – Amazon Shambhav 2024 (Top 0.01\% out of 100k+ applicants).\item Published paper at RDCAPE 2025 on machine learning in agriculture applications.\item Best Project Award – VeeyoTech 2024: Developed nutrition tracker with 93\% accuracy featuring AI-powered suggestions.\item Ranked top in 12 technical challenges and leadership contests, applying learnings to improve project effectiveness by 15\%.\end{itemize}\end{document}