\documentclass[a4paper]{article}\usepackage[top=0.3in, bottom=0.3in, left=0.5in, right=0.5in]{geometry}\usepackage{titlesec}\usepackage{enumitem}\usepackage{hyperref}\usepackage{parskip}\usepackage{xcolor}\usepackage{multicol}\usepackage{tabularx}\usepackage{tcolorbox}\usepackage{array}\usepackage{helvet}\renewcommand{\familydefault}{\sfdefault}\definecolor{lightgray}{gray}{0.9}\newtcolorbox{sectionbox}{colback=lightgray,colframe=white,boxrule=0pt,arc=0pt,left=4pt,right=4pt,top=1pt,bottom=1pt,width=\dimexpr\textwidth\relax}\hypersetup{colorlinks=true,urlcolor=blue,linkcolor=black}\setlength{\tabcolsep}{2pt}\renewcommand{\arraystretch}{0.9}\setlist[itemize]{leftmargin=1.5em, topsep=0pt, partopsep=0pt, itemsep=0.5pt, parsep=0pt}\titlespacing{\section}{0pt}{0.5pt}{0.5pt}\setlength{\parskip}{0pt}\begin{document}\vspace*{-0.3cm}\begin{center}{\LARGE\bfseries ARYAN KHUDLAIN}\\Delhi, India $\vert$ +91 7011085114 $\vert$ \href{mailto:aryankhudlain2004@gmail.com}{aryankhudlain2004@gmail.com}\\ \href{https://linkedin.com/in/aryankhudlain}{linkedin.com/in/aryankhudlain} $\vert$ \href{https://github.com/aryank2708}{github.com/aryank2708} \end{center}\begin{sectionbox}\textbf{EDUCATION}\end{sectionbox}\vspace{-0.3em}\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}\textbf{Netaji Subhas University of Technology (NSUT)}, Delhi & 2022 -- 2026 \\B.Tech in Information Technology & CGPA: 6.8 \\[0.5em]\textbf{Lancer's Convent}, Prashant Vihar & 2022 \\Senior Secondary (XII), CBSE & 92.4\% \\[0.5em]\textbf{Lancer's Convent}, Prashant Vihar & 2020 \\Secondary Education (X), CBSE & 89.2\% \\ \end{tabular*}\begin{sectionbox}\textbf{INTERNSHIPS AND EXPERIENCE}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Cyber Intern, IFSO/CCU – Delhi Police Special Cell} & Jun – Jul 2025 \\ \textit{Cyber Forensics and Research} & \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Engineered a Telegram forensic tool that accelerated digital investigations by \textbf{70\%}, enhancing case traceability and earning official commendation from Delhi Police.\item Leveraged forensic software (UFED, Autopsy, XRY, Oxygen Detective) to automate evidence analytics, reducing manual effort by \textbf{40\%} and improving data accuracy.\item Conducted in-depth research on cyber laws and profiling, contributing to the resolution of \textbf{4+} complex cases by enabling enhanced team collaboration and investigation clarity.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Software Development Intern, BoxPay Technologies Pvt. Ltd.} & Jun – Jul 2024 \\ \textit{Frontend \& UI Engineer – Founding Team Member} & \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Architected and delivered the company’s frontend portal using React.js and APIs, onboarding \textbf{50+} merchants with seamless digital wallet payment integration.\item Applied user-centered responsive UI design, improving customer retention by \textbf{40\%}, engagement, and overall satisfaction.\item Accelerated development workflows by \textbf{20\%} through efficient use of Chart.js and Figma prototypes, adhering to clean coding and agile practices.\end{itemize}\begin{sectionbox}\textbf{ACADEMIC PROJECTS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Telegram Data Export and Case Management Tool} &   \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Designed and implemented a forensic tool with a Tkinter GUI that reduced evidence processing time by \textbf{70\%}, streamlining critical investigative workflows.\item Integrated JSON export for secure, efficient local data storage, boosting documentation speed by \textbf{50\%} and improving case management usability by \textbf{40\%}.\item Ensured secure architecture and maintainability using Python, SQLite3, and Pandas, aligning project outcomes with compliance and productivity goals.\item \textbf{Tech Stack:} Python, Tkinter, SQLite3, Pillow, Pandas\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{NSUTTHON Website} &   \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Developed a full-stack platform using React.js and Node.js to centralize event registrations, increasing coordination efficiency by \textbf{40\%}.\item Enhanced user engagement through real-time updates, leaderboards, and schedules, raising participant interaction by \textbf{35\%}.\item Fostered cross-society collaboration by reducing manual communications by \textbf{50\%} via a unified interface.\item \textbf{Tech Stack:} React.js, Node.js, Express, PostgreSQL\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Walmart Sales Analysis} &   \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Analyzed multi-branch sales data utilizing Python and SQL, identifying peak sales hours and top categories to improve store revenue by \textbf{25\%}.\item Created interactive Python dashboards with Matplotlib and Seaborn, increasing business decision speed and insight accessibility by \textbf{30\%}.\item Automated reporting workflows by integrating SQL queries with Python scripts, reducing analysis time by \textbf{40\%}, improving operational efficiency.\item \textbf{Tech Stack:} Python, Pandas, Matplotlib, Seaborn, SQL, Jupyter Notebook\end{itemize}\begin{sectionbox}\textbf{SKILLS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}Programming Languages: & C, C++, JavaScript, SQL, HTML, Python \\Frameworks / Libraries: & React.js, Express.js, Node.js \\Tools / Databases: & GIT, GitHub, MySQL, PostgreSQL, MongoDB, Excel, Word, PowerPoint \\Soft Skills: & Graphic Design, Video Editing, Photography, Content Writing, Leadership \\ \end{tabularx}\begin{sectionbox}\textbf{POSITION OF RESPONSIBILITY}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{President, Crosslinks'25 – NSUT} & 2025 \\ \end{tabularx}\begin{itemize}\item Led and scaled a 20-member PR media team, increasing social media followers by \textbf{120\%} (from 2,500 to 5,500), enhancing community engagement and brand visibility.\item Strategized media coverage for \textbf{15+} events, expanding audience reach by \textbf{80\%} within one year through innovative communication and marketing techniques.\item Instituted workflow improvements reducing team onboarding duration by \textbf{35\%}, boosting operational agility and team efficiency.\end{itemize}\vspace{0.3em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Director of Performers, Shakesjeer'25 – NSUT} & 2025 \\ \end{tabularx}\begin{itemize}\item Organized and managed \textbf{10+} major performer events, improving live engagement and satisfaction by \textbf{30\%} through innovative content and coordination.\item Streamlined content creation, logistics, and outreach operations improving delivery efficiency by \textbf{25\%}.\item Enhanced performance quality by reducing errors and delays by \textbf{40\%} via optimized rehearsal and onboarding workflows.\end{itemize}\begin{sectionbox}\textbf{EXTRA-CURRICULARS \& ACHIEVEMENTS}\end{sectionbox}\vspace{0em}\begin{itemize}\item Awarded formal appreciation by NSUT for organizing Alumni Meet and Silver Jubilee events in 2023, demonstrating leadership and project management.\item Recognized officially by Delhi Police for impactful forensic contributions and development of investigation tools enhancing case resolutions.\item Represented Delhi in state-level Table Tennis tournaments, reflecting discipline, teamwork, and competitive drive.\item Secured Gold Medal in National Hindi Olympiad, showcasing academic excellence and strong language skills.\item Achieved 2nd place at NSUTTHON intra-college flagship event with Crosslinks, competing against 50+ teams.\end{itemize}\end{document}