\documentclass[a4paper]{article}\usepackage[top=0.3in, bottom=0.3in, left=0.5in, right=0.5in]{geometry}\usepackage{titlesec}\usepackage{enumitem}\usepackage{hyperref}\usepackage{parskip}\usepackage{xcolor}\usepackage{multicol}\usepackage{tabularx}\usepackage{tcolorbox}\usepackage{array}\usepackage{helvet}\renewcommand{\familydefault}{\sfdefault}\definecolor{lightgray}{gray}{0.9}\newtcolorbox{sectionbox}{colback=lightgray, colframe=white, boxrule=0pt, arc=0pt, left=4pt, right=4pt, top=1pt, bottom=1pt, width=\dimexpr\textwidth\relax}\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}\setlength{\tabcolsep}{2pt}\renewcommand{\arraystretch}{0.9}\setlist[itemize]{leftmargin=1.5em, topsep=0pt, partopsep=0pt, itemsep=0.5pt, parsep=0pt}\titlespacing{\section}{0pt}{0.5pt}{0.5pt}\setlength{\parskip}{0pt}\begin{document}\vspace*{-0.3cm}\begin{center}{\LARGE\bfseries Awab Mohamed}\\825-712-2707 $\vert$ \href{mailto:awabii-elradi112@hotmail.com}{awabii-elradi112@hotmail.com}\end{center}Driven and detail-oriented Computer Science major with extensive knowledge in security and safety. Fluent in Arabic; skillful in communicating and developing relationships with diverse groups. Possess over 2 years of experience in security, health \& safety, and warehouse operations, delivering excellent customer service and conflict resolution while adhering to safety protocols.\vspace{0.4em}\textbf{RELEVANT SKILLS AND ATTRIBUTES}\begin{itemize}\item Diligent - Consistently puts in effort and pays attention to detail to complete tasks effectively.\item Persistent - Keeps pushing forward despite obstacles or setbacks, demonstrating resilience.\item Self-motivated – Driven by internal goals and a strong work ethic to achieve results without needing constant supervision.\item Organized – Manages time and resources efficiently to prioritize tasks and meet deadlines.\item Proactive – Takes initiative to identify what needs to be done and acts promptly to accomplish goals.\end{itemize}\begin{sectionbox}\textbf{EDUCATION}\end{sectionbox}\vspace{-0.3em}\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}\textbf{Mount Royal University} & Anticipated Completion - 2027 \\Computer Science & \\\end{tabular*}\vspace{-0.2em}\begin{itemize}\item Completing courses in programming languages, algorithms, data structures, operating systems, software engineering, computer architecture, databases, and networking\end{itemize}\begin{sectionbox}\textbf{INTERNSHIPS AND EXPERIENCE}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Asset Protection Investigator, Hudson's Bay} & May 2023 - Present \\\textit{Calgary, AB} & \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item Patrol premises continuously to prevent theft, vandalism, and security breaches, reducing incidents by vigilance.\item Operate CCTV surveillance systems including Avigilon to monitor and document premises activities with accuracy.\item Identify and respond promptly to security incidents or emergencies, maintaining a safe environment.\item Detain individuals suspected of theft following legal protocols, ensuring compliance and safety.\item Compose detailed incident reports and maintain precise records, supporting organizational accountability.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Security Guard, Complete Security Solutions} & July 2021 - August 2024 \\\textit{Calgary, AB} & \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item Conduct regular patrols of assigned areas, maintaining security and safety standards throughout shifts.\item Manage access control by verifying IDs and regulating entry points to prevent unauthorized access.\item Utilize CCTV and security equipment to detect and report suspicious activities proactively.\item Respond swiftly to alarms, disturbances, or emergencies, minimizing potential risks.\item Draft thorough daily activity and incident reports, ensuring accurate documentation for safety compliance.\item Enforce company policies, safety regulations, and legal requirements consistently.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Warehouse Associate, Cadalow Halal Meat LTD} & August 2022 – August 2023 \\\textit{Calgary, AB} & \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item Operated electric forklift and power jack safely to unload and move customer orders efficiently in a fast-paced warehouse environment.\item Organized and processed customer invoices, clearing balances accurately using inventory and billing systems.\item Maintained efficient workflow by organizing invoices and paperwork, improving shipment processing times.\item Provided excellent customer service during unloading and order handling, contributing to customer satisfaction.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Sales Representative, Inner Circle Marketing [TNI Inc]} & May 2024 – February 2025 \\\textit{Calgary, AB} & \\\end{tabularx}\vspace{-0.2em}\begin{itemize}\item Conducted door-to-door outreach to prospective clients, presenting products and services effectively.\item Delivered clear product demonstrations and addressed customer inquiries to build trust and secure sales.\item Negotiated pricing and closed sales agreements, contributing to revenue growth and client base expansion.\end{itemize}\begin{sectionbox}\textbf{SKILLS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}Soft Skills: & Diligent, Persistent, Self-motivated, Organized, Proactive \\\end{tabularx}\begin{sectionbox}\textbf{EXTRA-CURRICULARS \& ACHIEVEMENTS}\end{sectionbox}\vspace{0em}\begin{itemize}\item Assisted individuals with questions and concerns at Stampede events, demonstrating strong interpersonal skills.\item Helped set up equipment for Mount Royal University's MSA Grand Iftar event, supporting event logistics.\item Provided security and directed patrons at BMO Centre during major events, ensuring safety and crowd control.\end{itemize}\vspace{0.4em}\textbf{TRAINING AND CERTIFICATES}\begin{itemize}\item First Aid and CPR\item WMHIS\item Alberta Basic Security License\item Class 5 Driver's License\item Conflict Resolution [Hudson's Bay]\item Harassment in Workplace [Hudson's Bay]\item Workplace Violence [Hudson's Bay]\end{itemize}\vspace{0.4em}\textbf{REFERENCES AND CREDENTIALS}\\\\* Available Upon request\end{document}