\documentclass[a4paper]{article} \usepackage[top=0.3in, bottom=0.3in, left=0.5in, right=0.5in]{geometry} \usepackage{titlesec} \usepackage{enumitem} \usepackage{hyperref} \usepackage{parskip} \usepackage{xcolor} \usepackage{multicol} \usepackage{tabularx} \usepackage{tcolorbox} \usepackage{array} \usepackage{helvet} \usepackage{calc} \renewcommand{\familydefault}{\sfdefault} \definecolor{lightgray}{gray}{0.9} \newtcolorbox{sectionbox}{ colback=lightgray, colframe=white, boxrule=0pt, arc=0pt, left=4pt, right=4pt, top=1pt, bottom=1pt, width=\dimexpr\textwidth\relax } \hypersetup{ colorlinks=true, urlcolor=blue, linkcolor=black } \setlength{\tabcolsep}{2pt} \renewcommand{\arraystretch}{0.9} \setlist[itemize]{leftmargin=1.5em, topsep=0pt, partopsep=0pt, itemsep=0.5pt, parsep=0pt} \titlespacing{\section}{0pt}{0.5pt}{0.5pt} \setlength{\parskip}{0pt} \begin{document} \vspace*{-0.3cm} \begin{center} {\LARGE\bfseries PIYUSH RAJ}\\ IT Student $\vert$ Delhi, India\\ +91-8860198815 $\vert$ \href{mailto:piyush65raj@gmail.com}{piyush65raj@gmail.com} $\vert$ \href{https://www.linkedin.com/in/piyush-raj-b22301229}{in LinkedIn} $\vert$ \href{https://github.com/PiyushRaj03}{GitHub} $\vert$ \href{https://piyushraj.in}{Portfolio} \end{center} \begin{sectionbox}\textbf{EDUCATION}\end{sectionbox} \vspace{-0.3em} \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r} \textbf{Netaji Subhas University of Technology, Delhi} & Nov 2022 -- Jun 2026 \\ B.Tech in \textit{Information Technology (Network Security)} & \\[0.5em] \end{tabular*} \begin{sectionbox}\textbf{EXPERIENCE}\end{sectionbox} \vspace{0em} \begin{tabularx}{\textwidth}{@{}X r@{}} \textbf{Product Intern} --- SalarySe & Dec 2024 -- Mar 2025 \\ \textit{Remote} & \end{tabularx} \vspace{-0.2em} \begin{itemize} \item Spearheaded integration of \textbf{RBL Bank credit card APIs and SDKs} into SalarySe app, enhancing payment solutions and driving \textbf{5,000+ card sales within 3 months}, reducing user drop-offs by \textbf{20\%} and improving client transaction success rate. \item Debugged and optimized \textbf{SBI card transaction flows} through Credilio platform, resolving \textbf{15+ critical issues}, boosting application success rate by \textbf{25\%} and reducing processing time by \textbf{30\%} to streamline customer experience. \item Conducted competitive analysis of \textbf{3+ rival platforms}, proposing \textbf{5+ UX enhancements} that were adopted in the product backlog, improving user journey alignment and stakeholder satisfaction. \end{itemize} \vspace{0.4em} \begin{sectionbox}\textbf{PROJECTS}\end{sectionbox} \vspace{0em} \begin{tabularx}{\textwidth}{@{}X r@{}} \textbf{Spotify Dashboard with AI Integration} $\vert$ \textit{Power BI, Python, OpenAI API} & \end{tabularx} \vspace{-0.2em} \begin{itemize} \item Designed and implemented an interactive \textbf{Spotify Analytics Dashboard} using Power BI for real-time visualization of song, artist trends, and user listening behavior. \item Integrated AI-powered insights leveraging Python scripts and OpenAI API to automate music recommendations and generate mood-based playlists, enhancing personalization accuracy. \item Applied advanced DAX measures and Power Query for data transformation and filtering, enabling predictive trend analysis and actionable business insights. \end{itemize} \vspace{0.4em} \begin{tabularx}{\textwidth}{@{}X r@{}} \textbf{Burger Bash Case Study} $\vert$ \textit{MySQL, SQL Workbench} & \end{tabularx} \vspace{-0.2em} \begin{itemize} \item Utilized SQL (JOIN, GROUP BY, ORDER BY, HAVING) to analyze delivery and sales datasets for Burger Runner, identifying key KPIs related to runner efficiency and customer purchase behavior. \item Generated and visualized business metrics through comprehensive MySQL queries, informing data-driven decision making and improving operational processes. \end{itemize} \begin{sectionbox}\textbf{SKILLS}\end{sectionbox} \vspace{0em} \begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}} Technical Skills: & SQL, Python, C++, Advanced Excel, Power BI, Tableau, Data Structures \& Algorithms, RDBMS Concepts, Microsoft Office. \\ Tools \& Platforms: & AWS, Azure, Google Cloud (Basic), Git, ETL Pipelines, Big Data Concepts, API Integration, GitHub Copilot, SQL Generation Tools. \\ Business \& Functional Skills: & Data Analysis, Business Requirements Gathering, Process Optimization, Decision-Making, Stakeholder Management, Communication, Risk Management. \\ \end{tabularx} \begin{sectionbox}\textbf{EXTRA-CURRICULARS \& ACHIEVEMENTS}\end{sectionbox} \vspace{0em} \begin{itemize} \item \textbf{EY Hackathon --- Team Lead:} Led 4-member team to \textbf{Top 47 out of 100,000+ participants}; achieved prototype accuracy of \textbf{92\%} by applying data-driven solution design. \item \textbf{TechSprint (SDA Bocconi Asia):} Awarded \textbf{3rd place} for developing a tool that enhanced resource efficiency; prize money 5000 INR. \item \textbf{Greentech Policy Case Competition (IIT Delhi, Tryst'24):} Placed \textbf{2nd nationally} for a sustainability-focused business revival strategy. \item \textbf{Pre-RMO \& Competitive Programming:} Ranked \textbf{Top 400 among 15,000+} in NBHM; solved \textbf{400+ problems} on Leetcode demonstrating strong algorithmic and problem-solving skills. \end{itemize} \begin{sectionbox}\textbf{POSITIONS OF RESPONSIBILITY}\end{sectionbox} \vspace{0em} \begin{tabularx}{\textwidth}{@{}X r@{}} \textbf{Core Team, Venatus Gaming Society -- Netaji Subhas University of Technology} & Sep 2023 -- Present \\ \end{tabularx} \begin{itemize} \item Organized gaming tournaments with \textbf{500+ participants} and secured \textbf{Rs 40,000+ in sponsorships}, growing membership by \textbf{35\%} through targeted engagement and collaboration. \end{itemize} \vspace{0.3em} \begin{tabularx}{\textwidth}{@{}X r@{}} \textbf{Student Member, IEEE -- NSUT Student Branch} & Aug 2022 -- Present \\ \end{tabularx} \begin{itemize} \item Facilitated \textbf{5 technical workshops} with \textbf{600+ attendees}; negotiated \textbf{Rs 50,000+} in sponsorships, enhancing knowledge-sharing and member participation. \end{itemize} \end{document}