\documentclass[a4paper]{article}\usepackage[top=0.3in, bottom=0.3in, left=0.5in, right=0.5in]{geometry}\usepackage{titlesec}\usepackage{enumitem}\usepackage{hyperref}\usepackage{parskip}\usepackage{xcolor}\usepackage{multicol}\usepackage{tabularx}\usepackage{tcolorbox}\usepackage{array}\usepackage{helvet}\renewcommand{\familydefault}{\sfdefault}\definecolor{lightgray}{gray}{0.9}\newtcolorbox{sectionbox}{colback=lightgray, colframe=white, boxrule=0pt, arc=0pt, left=4pt, right=4pt, top=1pt, bottom=1pt, width=\dimexpr\textwidth\relax}\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}\setlength{\tabcolsep}{2pt}\renewcommand{\arraystretch}{0.9}\setlist[itemize]{leftmargin=1.5em, topsep=0pt, partopsep=0pt, itemsep=0.5pt, parsep=0pt}\titlespacing{\section}{0pt}{0.5pt}{0.5pt}\setlength{\parskip}{0pt}\begin{document}\vspace*{-0.3cm}\begin{center}{\LARGE\bfseries JOHN DOE}\\San Francisco, CA $\vert$ (123) 456-7890 $\vert$ \href{mailto:john.doe@example.com}{john.doe@example.com}\\\href{https://linkedin.com/in/johndoe}{linkedin.com/in/johndoe} $\vert$ \href{https://github.com/johndoe}{github.com/johndoe}\end{center}\begin{sectionbox}\textbf{PROFESSIONAL SUMMARY}\end{sectionbox}\vspace{-0.3em}Experienced Data Scientist with over 8 years of expertise in designing, developing, and deploying machine learning models and data-driven solutions. Proven leader skilled in mentoring teams, collaborating across functions, and delivering scalable AI applications in production environments. Strong proficiency in Python, deep learning frameworks (TensorFlow, PyTorch), big data technologies, and statistical modeling. Passionate about advancing AI innovation and driving measurable business impact.\begin{sectionbox}\textbf{EXPERIENCE}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Senior Data Scientist, XYZ Analytics} & June 2018 -- Present\\\textit{San Francisco, CA} & \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Led end-to-end development and deployment of predictive models that increased client revenue by 22\% and reduced churn by 15\% using Python, Scikit-learn, and Spark.\item Mentored 5 junior data scientists, fostering continuous learning and improving team productivity by 30\% through structured knowledge sharing and code reviews.\item Collaborated cross-functionally with product, engineering, and business teams to define project scopes, resulting in a 40\% reduction in development cycles.\item Conducted exploratory data analysis, feature engineering, and validated models to ensure accuracy and robustness, achieving an average model AUC of 0.92.\item Integrated deep learning solutions with TensorFlow for image classification tasks, improving accuracy by 18\% over traditional methods.\item Led initiatives to deploy models into production environments using containerization and automated monitoring tools, reducing model latency by 25\%.\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Data Scientist, ABC Corp} & August 2014 -- May 2018\\\textit{San Jose, CA} & \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Developed and optimized machine learning models in Python and SQL that enhanced fraud detection rates by 28\% and lowered false positives by 12\%.\item Applied statistical modeling, experimental design, and causal inference techniques to improve campaign effectiveness, increasing ROI by 20\%.\item Led collaborative efforts with software engineers and product managers to translate complex data insights into actionable business strategies.\item Researched and implemented deep learning frameworks (PyTorch) for NLP projects, resulting in a 15\% improvement in sentiment analysis accuracy.\item Automated data pipelines and model deployment processes, increasing team efficiency and reducing manual errors by 35\%.\end{itemize}\begin{sectionbox}\textbf{EDUCATION}\end{sectionbox}\vspace{-0.3em}\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}\textbf{University of California, Berkeley} & Graduated May 2014\\Master of Science in Computer Science & \\[0.5em]\textbf{University of California, Berkeley} & Graduated May 2012\\Bachelor of Science in Statistics & \\\end{tabular*}\begin{sectionbox}\textbf{SKILLS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}Programming Languages: & Python, C++, JavaScript, SQL\\Data Analytics Tools: & Excel, Power BI, Pandas, NumPy, Matplotlib\\Databases: & MySQL, PostgreSQL, MongoDB, BigQuery\\Web Technologies: & HTML, CSS, React.js, Node.js, Express.js\\Version Control / Tools: & Git, GitHub, JIRA, Docker (Basics)\\Soft Skills: & Leadership, Teamwork, Problem-Solving, Communication\\\end{tabularx}\begin{sectionbox}\textbf{PROJECTS}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{ExpenseTracker Pro (Personal Project)} & \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Built a CLI-based personal expense tracker.\item Implemented persistent storage using SQLite3 for 5K+ entries.\item \textbf{Tech Stack:} Python, SQLite3, Pandas\end{itemize}\vspace{0.4em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Data Visualization Dashboard (Team Project)} & \end{tabularx}\vspace{-0.2em}\begin{itemize}\item Designed and deployed a Power BI dashboard for retail sales analysis.\item Automated ETL using Excel macros and SQL scripts.\item Reduced report generation time by \textbf{55\%}.\end{itemize}\begin{sectionbox}\textbf{POSITIONS OF RESPONSIBILITY}\end{sectionbox}\vspace{0em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{President, Tech Club – NSUT} & 2023 -- 2024\\\end{tabularx}\begin{itemize}\item Led a 15-member tech team organizing coding hackathons and seminars.\item Increased participation by \textbf{100\%} through online campaigns and events.\end{itemize}\vspace{0.3em}\begin{tabularx}{\textwidth}{@{}X r@{}}\textbf{Coordinator, Data Science Society} & 2022 -- 2023\\\end{tabularx}\begin{itemize}\item Managed operations for 10+ workshops on analytics and visualization.\item Raised sponsorship worth ₹50K by collaborating with industry partners.\end{itemize}\begin{sectionbox}\textbf{EXTRA-CURRICULARS \& ACHIEVEMENTS}\end{sectionbox}\vspace{0em}\begin{itemize}\item 2nd place at National DataHack 2024 among 400+ participants.\item Awarded for excellence in automation and leadership initiatives.\item Represented university in state-level Table Tennis championship.\end{itemize}\end{document}